Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-04-16 GWLDCII.tex
not-quite-right definition of inside/outside

Generally speaking the propagators are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator. As a general convention, we write $p = (i,j)$ with  $i < j$ relative to the first vertex. However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to vertices ``inside'' and ``outside'' the propagator); in this setting, we impose the convention that $p= (i,j)$ denotes a propagator flowing from $i$ to $j$, and $p= (j,i)$ denotes the \emph{same} propagator flowing in the opposite direction.

@@

By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.  This correspondence is given explicitly in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.

@@

@@

Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into three subsets of $[n]$, $\{[i+2, j-1], V(p), [j+2, i-1]\}$, the support of $p$ and the vertices that lie on either side of $p$. In the sequel we refer to the latter two intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.

\begin{dfn}\label{props inside p}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$. Write $(p, <_a)$ be the same propagator with a direction induced by the linear ordering $<_a$. Then \bas V_{in}(p, <_a) = \{b \in [n] | i+1 <_a b <_a j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_a) = \{b \in [n] | j+1 <_a b <_a i \} \;.\eas the region {\bf outside }$p$. 
\end{dfn}

Depending on the ordering associated to $p$, the vertices on the inside and outside chagne. In particular, for $p = (i,j)$, $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.

This in turn defines two sets of propagators, $\{\cP_{in}(p, <_i), \cP_{out}(p, <_i)\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas When clear, we drop the parentetical and just write $\cP_{in}$ (resp. $\cP_{out}$). These sets are the sets of propagators, not equal to $p$, \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp. $V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are neither on the inside and outside of $p$. Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$. Under these circumstances, the set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side. In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$. Recall from Definition~\ref{admisdfn} that a {\em weakly admissible} diagram is one that satisfies the density and non-crossing conditions but does not require that $|V(\cP)| \geq |\cP| + 4$.

As with the vertex sets,  which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.

\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
\[\ell(p) = min\big\{|V_{in}(p)|,|V_{out}(p)|\big\} +2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}
In other words, $\ell(p)$ is the size of the smaller of the number of vertices that lie on either side of the progator $p$.

\begin{rmk}\label{rem:props of length 2 and 3} 
The following observations about configurations of propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
\begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
\end{enumerate}
\end{rmk}

@@

Now suppose $W$ has no propagators of length $3$.
%  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
%\begin{equation}\label{eq:2 prop config}
%\begin{tikzpicture}[baseline=(current bounding box.east)]
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{20}
%
%\begin{scope}
%\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
%
%\begin{scope}
%\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%
%% vertices
%\foreach \i in {2,3,...,7}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%
%\begin{scope}
%\clip (0,0) circle[radius=\radius];
%\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
%\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
%
%\end{scope}
%
%\node at (80:\radius*1.1) {\tiny $j$};
%\node at (100:\radius*1.1) {\tiny $j+1$};
%\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
%
%\end{scope}
%\end{tikzpicture}
%\end{equation}

We need a bit of notation: Let $W = (\cP, n)$ a weakly admissible Wilson loop diagram, and $Q \subseteq \cP$. Define the restriction $W|_Q$ to be the diagram $W$ with the propagators not in $Q$ removed. That is , \bas W|_Q = (Q, n). \eas

%to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.  Denote this diagram by $W_{[i,j]}$. That is, if $W = (\cP, n)$ is a Wilson loop diagram, \bas W_{[i,j]} = (\cP \setminus \Prop([i,j]^c), n)\eas

Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$. That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself. \footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$. That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$. }

@@

With these observations in mind we can return to the proof.

We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $\{p_1, \ldots, p_r\}$ and $\{q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}
Note that we will be interested in the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are on the outside of $q_r$.
By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

@@

INSERT PICTURE HERE?

@@

%% this was 100% a productive use of my time
%\[\begin{tabular}{ccc}
%% possibility 1
%\begin{tikzpicture}
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{15}
%\begin{scope}
%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
%% vertices 
%\foreach \i in {2,3,4,6,7,8,9,10}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%% \dots 
%\foreach \i in {1,2,3}{
%	\node at (65 + \i*5:\radius cm) {$\cdot$};
%}
%\begin{scope} % this scope contains the propagators
%\clip (0,0) circle[radius=\radius];
%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
%\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
%% grey prop begins here
%\begin{scope}
%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
%\end{scope}
%\begin{scope}
%\clip (0,0) circle[radius=\radius];
%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
%\end{scope}
%\begin{scope}
%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
%\clip (0,0) circle[radius=\radius];
%\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
%\end{scope}
%% end gray prop
%\end{scope}
%\node at (90:\radius*0.30 cm) {\tiny $q_r$};
%\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
%\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
%% circle/edges; needs to happen last to overlap gray
%\begin{scope}
%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%\end{scope} % ends the overall rectangle clipping
%\end{tikzpicture}
%&
%% possibility 2
%\begin{tikzpicture}
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{15}
%\begin{scope}
%% overall clipping to make the size sensible
%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
%% vertices
%\foreach \i in {2,3,4,6,7,8,9,10}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%% \dots
%\foreach \i in {1,2,3}{
%	\node at (65 + \i*5:\radius cm) {$\cdot$};
%}
%\begin{scope} % props
%\clip (0,0) circle[radius=\radius cm]; 
%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
%\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
%%% grey prop starts here
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
%\end{scope}
%\begin{scope}
%\clip (0,0) circle[radius=\radius];
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
%\end{scope}
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
%\clip (0,0) circle[radius=\radius];
%\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
%\end{scope}
%% grey prop ends here
%\node at (90:\radius*0.32 cm) {\tiny $q_r$};
%\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
%\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
%% circle/edges
%\begin{scope}
%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%\end{scope} % ends overall clip
%\end{tikzpicture}
%&
%% possiblitiy 3
%\begin{tikzpicture}
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{12}
%\begin{scope}
%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
%% vertices
%\foreach \i in {2,3,6,7,8,9,12,13}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%% \dots
%\foreach \i in {1,2,3}{
%	\node at (44 + \i*5:\radius cm) {$\cdot$};
%	\node at (116 + \i*5:\radius cm) {$\cdot$};
%}
%\begin{scope} % props
%\clip (0,0) circle[radius=\radius cm];
%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
%\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
%%  grey prop 1
%% not q_{r+1}
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
%\end{scope}
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
%\end{scope}
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
%\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
%\end{scope}
%% grey prop 1 ends here
%% grey prop 2
%% this is q_{r+1}
%\begin{scope}
%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
%\end{scope}
%\begin{scope}
%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
%\end{scope}
%\begin{scope}
%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
%\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
%\end{scope}
%% grey prop 2 ends here
%\end{scope}
%\node at (90:\radius*0.15 cm) {\tiny $q_r$};
%\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
%\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
%\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
%% overall circle
%\begin{scope}
%\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%\end{scope} % ends overall clip
%\end{tikzpicture}
%\end{tabular}
%\]
%In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.  In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.

@@

Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the algorithm assigns $i$ to $p$.  The answer is that the set is a non-empty cyclic interval.  Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.

@@

%Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas
%\begin{dfn}\label{protect dfn}
%Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
%\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
%\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
%\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$. In this case, $P_w(p) = \emptyset$. When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
%\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}. \eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
%\end{enumerate}
%\end{dfn}
%The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$. Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$. We place the restrictions on the vertex $a$ as follows: \begin{enumerate} \item $P_v$ prevents $p$ from contributing to $I_a$ if \bas i_{s_r}  <_{v+1} a-1 <_{v+1} v\eas \item $P_{v+1}(p)$ prevents $p$ from contributing to $I_a$ only if $P_v(p)$ prevents $p$ from contributing $v$ to $I_a$. \end{enumerate}
%\begin{eg} \label{eg: protective sets}
%Consider the admissible Wilson loop diagram
%\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
%	\begin{scope}
%	\drawWLD{17}{3}
%	\drawnumbers
%	\drawprop{1}{0}{16}{0}
%	\drawlabeledprop{2}{0}{15}{1}{p}
%    \drawprop{6}{2}{15}{0}
%    \drawprop{3}{0}{6}{1}
%    \drawprop{4}{0}{6}{0}
%    \drawprop{7}{0}{11}{0}
%    \drawprop{8}{0}{10}{0}
%    \drawprop{11}{1}{14}{1}
%    \drawprop{12}{0}{14}{0}
%		\end{scope}
%	\end{tikzpicture}
%\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$. The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$. There is no set preventing $p$ from contributing $16$ to $I_{15}$. At $a = 9$, the set $P_{15} = \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = Q$, though the other two propagators in the set prove unnecessary to keep $p$ from contributing $15$ to $I_{9}$. At $a = 14$, both $P_{15}$ and $P_{16}$ exists, with $P_{15} = \{(11, 14), (12, 14)\} \subset R $ and $P_{16}= \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.
%Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
%\end{eg}
%\begin{lem}\label{protecting lem}
%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex. For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above. Then $p$ does not contribute $v$ to $I_a$ if $i_{s_r} +1 <_{v+1} a <_{v+1} v+1 $. If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
%Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$. Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.
%Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}. Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$. Then $s_x$ cannot contribute to $I_a$ before vertex $v$. By construction $P_{i_{s_x}+1}(s_{x-1})\subset P_v(p)$. Therefore, $s_{x-1}$ does not contribute $i_{s_x}+1$ to $I_a$. Thus we conclude that $s_1$ does not contribute $i_{s_1}$ or $i_{s_1}+1$ to $I_a$. In other words, $s_1$ has not been removed from the diagram at vertex $v$.
%Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.
%\begin{cor} \label{protecting cor}
%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$. If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
%\end{cor}
%Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
%The converse, however requires an extra condition.
%\begin{lem} \label{protect conv lem}
%For $W = (\cP, [n])$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp. $v+1$) is the first vertex of $V(p)$ in the $<_a$ order such that $P_v$ (resp. neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp. $v+1$) to $I_a$.
%Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
%If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)
%If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp. $i_{t_1}$ or $i_{t_1}+1$) to $I_a$. Then one of the following three situations hold: \begin{enumerate} \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v$: In this case, $s_1$ cannot be removed until $v$. \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v-1$: in this case there exists a propagator $s_2 = (i_{s_2}, j_{s_2})$ with $i_{s_1} \leq_{v+1} i_{s_2} <_{v+1} j_{s_2}$ and $j_{s_2} \in \{j_{s_1}-1, j_{s_1}\}$. \item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}
%However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$. One does this by a similar construction to above. In this manner, we begin to build the sets $P_v(p)$ and $P_{v+1}(p)$.  By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.
%We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction. For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction. That is, for $0 < k < m$, $p_k \in \{s_k, t_k\}$. Futher define $p_0 = p$.
%%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}
%If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.
%If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
% \begin{description}

>>>>

Generally speaking the propagators are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator. As a general convention, we write $p = (i,j)$ with  $i < j$ relative to the first vertex. However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to the regions ``inside'' and ``outside'' the propagator); in this setting, we write $(p,<_i)$ to indicate that $p$ is directed from $i$ to $j$, and $(p,<_j)$ for the same propagator directed from $j$ to $i$.

@@

By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.  This correspondence is given explicitly in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
\[\cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.

@@

\subsection{Wilson loop diagrams as positroids}\label{sec:WLD as positroids}

@@

\begin{dfn}\label{props inside p}
Let $W = (\cP, [n])$ be a weakly admissible Wilson loop diagram, with $p \in \cP$ supported on edges $i$ and $j$. Write $(p, <_i)$ to be the same propagator with a direction induced by the linear ordering $<_i$. Then
\begin{gather*}\cP_{in}(p,<_i) = \{ q \in \cP \ |\ (q,<_i) = (k,l) \text{ and }i \leq_i k <_i l \leq_i j \} \\
\cP_{out}(p,<_i) = \{ q \in \cP \ | \ (q,<_i) = (k,l) \text{ and } j \leq_i k <_i l  \} \;\end{gather*}
are the sets of propagators inside (resp. outside) $p$. \note{by this definition, $p \not\in \cP_{out}$}
\end{dfn}

% Observe that changing the direction of the propagator simply swaps the inside and outside sets, i.e. for $p = (i,j)$ we have 
% \[\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\quad \text{ and } \quad \cP_{out}(p, <_i) = \cP_{in}(p, <_j).\]

\begin{dfn}
Let $p = (i,j) \in \cP$ be a propagator in $W$.  Define the {\bf length} of $p$ to be 
\[\ell(p) \  =\ \min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}
In other words, $\ell(p)$ is the size of the smaller of the sets of vertices on either side of the propagator $p$.

\begin{rmk}\label{rem:props of length 2 and 3} 
The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
\begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
\end{enumerate}
\end{rmk}

@@

Now suppose $W$ has no propagators of length $3$.

Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can construct two obvious subdiagrams of $W$ by removing all of the propagators on one side of $p$ and leaving the vertices intact, i.e. the subdiagrams
\[  (\cP_{in}\cup\{p\}, [n])  \quad \textrm{and} \quad  (\cP_{out}\cup \{p\}, [n]).\]

%where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$. That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself. 
%\footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$. That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$. }

@@

%With these observations in mind we can return to the proof.

We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $\{p_1, \ldots, p_r\}$ and $\{q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}
We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and 
By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

@@

\hlfix{INSERT PICTURE HERE?}{note highlighting this for anyone skimming through looking for pictures to add}

@@

@@

Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.  The answer is that the set is a non-empty cyclic interval.  Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.

@@
